\documentclass[a4paper,english,bookmarks]{article}
\usepackage{./Structure/4PE18TEXTB}
\usepackage{marginnote}

\begin{document}

\stylizeDoc{English}{Lesson}{Tuesday 12 April 2022}
\newboxans

\hfill\newline

\section*{\centering\EBGaramond\Large\itshape Test de vocabulaire}

4NMWK2 : 2R4

\section*{\centering\EBGaramond\Large\itshape Universal Basic Income}

For Decades, the minimum wage has 
The Covid-19 pandemy and president Joe Biden push 

Economist believe it result in Job Loses. Today 90\% of countries 

for more than 100 years, workers fought for 

Australia first introduced

Most economist believes it could

\boxans{
    Common wisdom considers that increasing the minimum wage can cause job losses -> It's DETRIMENTAL to everyone : employee may be fired, unemployee can not find job.
    
    When was it record-high ? During the Great Depression (1930s), and then there have been decades of it going down.
    
    Are all states the same ? No ! They can dedice to have higher wages than the federal minimum (5 of them do). A PATCHWORK of situations.
    
    What doesresearch suggest ? In 1992, there was a comparative study. New Jersey had a higher minimum wage than Pennsylvania... but they had a higher employment rate.
    
    CCL : findings are COUNTER-INTUITIVE, and sometimes inconclusive.
}

\section*{\centering\EBGaramond\Large\itshape A Modest Proposal for Preventing the Children of Poor People from Being a Burden on their Parents or Country, Jonathan Swift 1729}

It is a great pity that, although we have found many uses for the resources of the African continent, we do not know what to do with its people. Asian children are, for example, very useful in the textile and new technology industries. This problem is made worse by the fact that the African population does not live in luxury, and especially because of its large population growth, is starving because it cannot feed itself with the generous resources we leave them.

\end{document}